### 2020-04-22 final_report/conclusion.tex

Over the course of this internship project, we employed a broad spectrum of data analysis and machine learning techniques to develop fast and high-quality surrogate models for a MC TBR model in use at UKAEA. 
---

---
After a thorough review of the literature, we developed a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models. Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioral trends over its hyperparameters which are consistent with the design of the algorithm.

>>>>

Over the course of this internship project, we employed a broad spectrum of data analysis and machine learning techniques to develop fast and high-quality surrogate models for a MC TBR model in use at UKAEA. We generated 900,000 samples for training and test purposes, evaluated on this expensive MC model. We investigated possibilities for simplification of the parameter space, and concluded that no straightforward reduction was possible. After reviewing $N$ surrogate models (fill in $N$), and examining their behaviour on (un)constrained feature space and scaling properties, we retrained some of the best-performing surrogates on the full parameter space. The optimum results obtained were an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model.

After a thorough review of the literature, we also developed a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models. Preliminary testing on a toy theory, qualitatively comparable to the MC TBR model, demonstrated the effectiveness of QASS and behavioural trends consistent with the design of the algorithm. $Insert numerical results for QASS.$ Further optimisation over the hyperparameter space has strong potential to increase this performance, allowing for future deployment of QASS on the MC TBR model in coalition with any of the most effective identified surrogate models.

### 2020-04-22 final_report/introduction.tex
harmonize references in favour of \cref

Nuclear fusion technology relies on the production and containment of an
extremely hot and dense plasma. In this environment, by design similar to that
of a star, hydrogen atoms attain energies sufficient to overcome their usual
electrostatic repulsion and fuse to form helium \cite{Hernandez2018}. Early prototype reactors
made use of the deuterium (\isotope[2]{H}) isotope of hydrogen in order to
achieve fusion under more accessible conditions, but achieved limited success.
The current frontier generation of fusion reactors, such as JET and the
under-construction International Thermonuclear Experimental Reactor (ITER), make
use of tritium (\isotope[3]{H}) fuel for further efficiency gain.
Experimentation at JET dating back to 1997 \cite{Keilhacker1999} has made significant headway in
validating deuterium-tritium (D-T) operations and constraining the technology
which will be employed in ITER in a scaled up form.

However, tritium is much less readily available as a fuel source than deuterium.
While at least one deuterium atom occurs for every 5000 molecules of
naturally-sourced water, and may be easily distilled, tritium is extremely rare
in nature. It may be produced indirectly through irradiation of heavy water
(deuterium oxide) during nuclear fission, but only at very low rates which could
never sustain industrial-scale fusion power.

@@

The TBR is defined as the ratio between tritium generation in the breeding
blanket per unit time and tritium fuel consumption in the reactor. The MC
neutronics simulations previously mentioned therefore must account for both the
internal plasma dynamics of the fusion reactor and the resultant interactions of
neutrons with breeding blanket materials. Neutron paths are traced through a CAD
model (e.g. \cref{fig:tokamak}) of a reactor with modifiable geometry.

>>>>

Nuclear fusion technology relies on the production and containment of an
extremely hot and dense plasma. In this environment, by design similar to that
of a star, hydrogen atoms attain energies sufficient to overcome their usual
electrostatic repulsion and fuse to form helium \cite{Hernandez2018}. Early prototype reactors
made use of the deuterium (\isotope[2]{H}, or \isotope{D}) isotope of hydrogen in order to
achieve fusion under more accessible conditions, but lead to limited success.
The current frontier generation of fusion reactors, such as JET and the
under-construction International Thermonuclear Experimental Reactor (ITER), make
use of tritium (\isotope[3]{H}, or \isotope{T}) fuel for further efficiency gain.
Experimentation at JET dating back to 1997 \cite{Keilhacker1999} has made significant headway in
validating deuterium-tritium (D-T) operations and constraining the technology
which will be employed in ITER in a scaled up form.

However, tritium is much less readily available as a fuel source than deuterium.
While at least one deuterium atom occurs for every \num{5000} molecules of
naturally-sourced water, and may be easily distilled, tritium is extremely rare
in nature. It may be produced indirectly through irradiation of heavy water
(\ce{D2O}) during nuclear fission, but only at very low rates which could
never sustain industrial-scale fusion power.

@@

The TBR is defined as the ratio between tritium generation in the breeding
blanket per unit time and tritium fuel consumption in the reactor. The MC
neutronics simulations previously mentioned therefore must account for both the
internal plasma dynamics of the fusion reactor and the resultant interactions of
neutrons with breeding blanket materials. Neutron paths are traced through a CAD
model (e.g.~\cref{fig:tokamak}) of a reactor with modifiable geometry.

### 2020-04-22 final_report/tbr_final_report-metadata.tex
Added bibliography .bib file
Remove URLS and DOI from visible bibliography.
add bitmap ukaea logo placeholder, enable draft mode

% Partner Logo
% put the name of the logo image file found in graphics path
%\DISPartnerLogo{path/to/logo/image}

% Title
\DISTitle{Results from TBR Group Project}

% Draft version:
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\DISVersion{0}

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
  The abstract of my report.
}

@@

% DIS reference code if ever used
\DISRefCode{UCLCDTDIS-2019-XX}

>>>>

% Partner Logo
% put the name of the logo image file found in graphics path
% TODO: make this a vector logo, wait for reply from Vignesh
\DISPartnerLogo{ukaea_logo}

% Title
\DISTitle{Surrogate Modelling of\\the Tritium Breeding Ratio}

% Draft version:
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% TODO: Comment or remove in final version.
\DISVersion{0}

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
  Surrogate modelling techniques have been employed in diverse areas of research to resolve the limitations of resource-expensive procedure with significantly cheaper approximations. In this internship project, we sought to develop a fast and high-quality surrogate model for simulations of the tritium breeding ratio (TBR) for under-design Tokamak nuclear fusion reactors. We investigated possibilities for dimensional reduction on the parameter space of a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We investigated possibilities for dimensional reduction on the parameter space of this model, and reviewed $N$ classes of surrogate models for potential applicability. Here we present the performance and scaling properties of these surrogate models, the best of which demonstrated an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model. We further present a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models. Our preliminary testing on a toy TBR theory has demonstrated the efficacy of this algorithm for speeding up the surrogate modelling process.
}

@@

% DIS reference code if ever used
%\DISRefCode{UCLCDTDIS-2019-XX}
